---
title: "Regression analysis"
output:
  html_document:
    df_print: paged
  pdf_document: default
bibliography: ref.bib
---

```{r}
df <- read.csv(file = "data_econ.csv")
head(df)
```

# Correlation of treatments

We first check the independence between the treatments. This serves as a sanity check as the treatments are assigned in a random manner.

```{r}
# remove the first two column
R.hat <- cor(df[df["treatment"] == 1, c("ask", "ratio", "size")]) 
print(R.hat)
```

# Using Probit model to regress the response probability with treatments (repeats [\@karlan2007original])

Check the marginal effects over all samples as in [\@karlan2007original], Table 3.

```{r}
library("mfx")

model.probit <- probitmfx(gave ~ treatment,
    data = df)
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df)
model.probit
```

Check the marginal effects over samples who Already Gave in 2005.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df[df["dormant"] == 1,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df[df["dormant"] == 1,])
model.probit
```

Check the marginal effects over samples who Had Not Given Yet in 2005.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df[df["dormant"] == 0,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df[df["dormant"] == 0,])
model.probit
```

Check the marginal effects over samples who Below Median Prior Donor ($<$\$35).

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df[df["ltmedMRA"] == 1,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df[df["ltmedMRA"] == 1,])
model.probit
```

Check the marginal effects over samples who Above Median Prior Donor ($\ge$\$35)

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df[df["ltmedMRA"] == 0,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df[df["ltmedMRA"] == 0,])
model.probit
```

# Using OLM to regress the amount given with treatments (repeats [\@karlan2007original])

This section tries to regress the amount given with respect to the treatments. This part repeats the results in [\@karlan2007original], Table 4. The computation is too long so only a small portion is reproduced.

```{r}
model.lm <- lm(amount ~ treatment.fac, data = df[df["gave"] == 1,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df[df["gave"] == 1,])
summary(model.lm)
```

# Using the Probit model to check the response rate more subgroups (new insights)

```{r}
df.updated <- read.csv(file = "AER merged.csv")
# get median of median_hhincome, ave_hh_sz
median.mhi <- median(df.updated[,"median_hhincome"], na.rm = TRUE)
median.ahs <- median(df.updated[,"ave_hh_sz"], na.rm = TRUE)
# binarized subgroups based on median
df.updated["high_income"] <- as.integer(df.updated[,"median_hhincome"] >= median.mhi)
df.updated["large_family"] <- as.integer(df.updated[,"ave_hh_sz"] >= median.ahs)
# preview part of the data
head(df.updated)
```

```{r}
hist(df.updated$median_hhincome, main="", xlab="Median household income", freq = FALSE)
abline(v=median.mhi, col="red", lwd = 2)
hist(df.updated$ave_hh_sz, main="", xlab="Average household size", freq = FALSE, breaks = 20)
abline(v=median.ahs, col="red", lwd = 2)
```

## Relationship between median household income and average household size

```{r}

plot(ave_hh_sz ~ median_hhincome, data = df.updated, col = "grey", pch = 20,
     xlab = "Median household income (MHI)", ylab = "Average household size (AHS)")
fit_1 = lm(ave_hh_sz ~ median_hhincome, data = df.updated)
abline(fit_1, col = "darkorange", lwd = 3)


model.mhi.ahs <- lm(ave_hh_sz ~ median_hhincome, data = df.updated)
plot(model.mhi.ahs, which=1)
```

## Gender

Female, response rate.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df.updated[df.updated["female"] == 1,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df.updated[df.updated["female"] == 1,])
model.probit
```

Male, response rate.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df.updated[df.updated["female"] == 0,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df.updated[df.updated["female"] == 0,])
model.probit
```

## Median Household Income

Low median household income, response rate.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df.updated[df.updated["high_income"] == 0,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df.updated[df.updated["high_income"] == 0,])
model.probit
```

High median household income, response rate.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df.updated[df.updated["high_income"] == 1,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df.updated[df.updated["high_income"] == 1,])
model.probit
```

## Average household size

Large household size, response rate.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df.updated[df.updated["large_family"] == 1,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df.updated[df.updated["large_family"] == 1,])
model.probit
```

Small household size, response rate.

```{r}
model.probit <- probitmfx(gave ~ treatment,
    data = df.updated[df.updated["large_family"] == 0,])
model.probit

model.probit <- probitmfx(gave ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100,
    data = df.updated[df.updated["large_family"] == 0,])
model.probit
```

# Using OLM to regress the amount given with treatments (new insights)

## Gender

Male.

```{r}
model.lm <- lm(amount ~ treatment, data = df.updated[df.updated["female"] == 0,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df.updated[df.updated["female"] == 0,])
summary(model.lm)
```

Female.

```{r}
model.lm <- lm(amount ~ treatment, data = df.updated[df.updated["female"] == 1,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df.updated[df.updated["female"] == 1,])
summary(model.lm)
```

## Median Household Income

Low MHI.

```{r}
model.lm <- lm(amount ~ treatment, data = df.updated[df.updated["high_income"] == 0,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df.updated[df.updated["high_income"] == 0,])
summary(model.lm)
```

High MHI.

```{r}
model.lm <- lm(amount ~ treatment, data = df.updated[df.updated["high_income"] == 1,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df.updated[df.updated["high_income"] == 1,])
summary(model.lm)
```

## Average Household Size

Low AHS,

```{r}
model.lm <- lm(amount ~ treatment, data = df.updated[df.updated["large_family"] == 0,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df.updated[df.updated["large_family"] == 0,])
summary(model.lm)
```

High AHS.

```{r}
model.lm <- lm(amount ~ treatment, data = df.updated[df.updated["large_family"] == 1,])
summary(model.lm)

model.lm <- lm(amount ~ treatment + askd2 + askd3 + ratio2 + ratio3 + size25 + size50 + size100, data = df.updated[df.updated["large_family"] == 1,])
summary(model.lm)
```
